---
title: 'MA615: Text Analysis'
author: "Yongrong Chai"
date: "11/29/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE, comment = NA}
knitr::opts_chunk$set(echo = TRUE,out.width="0.9\\linewidth",dev="pdf",fig.align  = 'center')
pacman::p_load(
  "ggplot2",
  "knitr",
  "VGAM",
  "rvest",
  "tidyverse",
  "wordcloud",
  "dplyr",
  "tidytext",
  "stringr",
  "tidyr",
  "scales",
  "gridExtra",
  "magrittr",
  "sentimentr"
)
#devtools::install_github("Truenumbers/tnum/tnum")
```

This is a sentiment analysis of Anne of Green Gables by Lucy Maud Montgomery.
```{r, echo=FALSE}
anne <- read_html("https://www.gutenberg.org/cache/epub/45/pg45-images.html")
read_anne <- anne %>%
 html_nodes("p") %>%
 html_text()

#transfer into a data frame
anne_ <- data_frame(line = 1:1786, text = read_anne) #whole size1786
#remove empty lines
anne_ <- anne_ %>% filter(text != "")
#a token per row
anne_ <- anne_ %>%unnest_tokens(word,text)
#omit non-characters
anne_ <- anne_ %>% mutate(word = str_extract(word,"[a-z']+"))
anne_ <-na.omit(anne_)
#omit stop-words
anne_<- anne_ %>% anti_join(stop_words)
```

## Overall Word Count
```{r, echo=FALSE}
library(tidytext)
#overall word count
anne1 <- anne_ %>%
count(word, sort = TRUE)%>%
  filter(n > 100) %>%
  mutate(word = reorder(word, n))
anne1 %>% ggplot(aes(word, n)) +geom_col() +xlab(NULL) +coord_flip() + ggtitle("Word Count for Anne of Green Gables")
```
Top 4 words in book are
Anne: protagonist is Anne
Marilla: Although she is not the protagonist's biological mother, she is like Anne's mother.
Diana:Anne's best friend
Matthew: Marilla's brother, he is like Anne's father.


## Positive word count V.S. negative word count
```{r, echo=FALSE}
#Positive word count
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "positive")

anne2 <- anne_ %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)%>%
  filter(n > 30) %>%
  mutate(word = reorder(word, n))
p1<-anne2 %>% ggplot(aes(word, n)) +geom_col() +xlab(NULL) +coord_flip() +ggtitle("Positive Word Count for\nAnne of Green Gables")

#negative word count
nrc_neg <- get_sentiments("nrc") %>% 
  filter(sentiment == "negative")

anne2 <- anne_ %>%
  inner_join(nrc_neg) %>%
  count(word, sort = TRUE)%>%
  filter(n > 20) %>%
  mutate(word = reorder(word, n))
p2<-anne2 %>% ggplot(aes(word, n)) +geom_col() +xlab(NULL) +coord_flip() +ggtitle("Negative Word Count for\n Anne of Green Gables")
grid.arrange(p1, p2, ncol=2)
```

The main plot of this book:
Anne is an orphan who is adopted by Matthew and Marilla and grows up on their farm, Green Gables. 
Positive words here show the joy of growing up as a little girl. Cold words here shows Anne, as an orphan, just arrived in a new environment of loneliness, exclusion, re-establish the world view of helplessness at the beginning.


## Comparing the three sentiment dictionaries
```{r, echo=FALSE}
get_sentiments("afinn")
get_sentiments("nrc")
get_sentiments("bing")

afinn <- anne_ %>% 
  inner_join(get_sentiments("afinn")) %>% 
                 #filter(sentiment %in% c("positive", 
                                        # "negative")) %>%
  group_by(index = line %/% 10) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")


bing_and_nrc <- bind_rows(
  anne_ %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  anne_ %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = line %/% 10, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```




## Most common positive and negative words
```{r, echo=FALSE}
bing_word_counts <- anne_ %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

#Remove stop words "miss"
custom_stop_words <- bind_rows(tibble(word = c("miss"),  
                                      lexicon = c("custom")), 
                               stop_words)

#custom_stop_words
```

## Word Clouds
```{r, echo=FALSE, warning=FALSE, comment = NA}
anne_ %>%
  anti_join(custom_stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

```


```{r, echo=FALSE, warning=FALSE, comment = NA, fig.width=10, fig.height=10}
library(reshape2)

anne_ %>% anti_join(custom_stop_words)%>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

Positive words are obviously much larger than negative words. As a children book, the whole book is about family, friendship and childhood, which is why there are more positive words.

## Reference: 
https://www.r-bloggers.com/2020/04/sentiment-analysis-in-r-with-sentimentr-that-handles-negation-valence-shifters/ 
https://www.gutenberg.org/ebooks/45 https://learn.bu.edu/ultra/courses/_80585_1/cl/outline 
https://www.tidytextmining.com/sentiment.html


